### 2017-11-22 manuscript.rmd
added align function to phylosig xtable

#####Phylogenetic signal in Binary Traits
```{r phylosig_binaries, echo=F, message=F, warning=F}
 # make it xtable
xtable_PS<-xtable(binaries_phylosig,auto=TRUE)
print(xtable_PS, scalebox=0.7)
```

>>>>

#####Phylogenetic signal in Binary Traits
```{r phylosig_binaries, echo=F, message=F, warning=F}
 # make it xtable
xtable_PS<-xtable(binaries_phylosig,auto=TRUE)
align( xtable_PS ) <- c('l|',rep('p{0.5in}',ncol(binaries_phylosig)) )
print(xtable_PS, scalebox=0.7)
